Data Exploration

### 2019-01-09 src/data_exploration.Rmd
background correlations rerun with corrected data

```{r}
background <- read.csv("../output/bio/background_complete_obs_cels.csv", header = TRUE)
head(background)
test <- background[245:250, ]
test
```

@@

@@

```{r}
kruskal.test(presence$temp_celsius_depth ~ presence$gear)
```
Ok so there is a statistically sig difference somewhere in the temp at depth reported by the gear type (Kruskal-Wallis chi-squared = 248.27, df = 7, p-value < 2.2e-16)

To see where the difference(s) are run a Dunn test Zar (2010) states that the Dunn test (in the FSA package) is appropriate for groups with unequal numbers of observations.(Zar, J.H. 2010. Biostatistical Analysis, 5th ed.  Pearson Prentice Hall: Upper Saddle River, NJ.)

SAM WHEN DUNN IS INSTALLED, GO TO RCOMPANIONS.ORG AND LOOK FOR DUNN - CHECK CHROME HISTORY (PROBABLY UNDER KRUSKAL WALLIS) ALSO MAP THE DISTRIBUTION OF THESE GEAR TYPES
```{r}
pairwise.wilcox.test(presence$temp_celsius_depth, presence$gear, p.adj='bonferroni', exact=F)
```

>>>>

```{r}
background <- read.csv("../output/bio/background_complete_obs_cels.csv", header = TRUE)
head(background)
#test <- background[245:250, ]
#test
```

@@

check to see if there are any correlations in the env. variables for the background points

@@

```{r}
kruskal.test(presence$temp_depth ~ presence$gear)
```
Ok so there is a statistically sig difference somewhere in the temp at depth reported by the gear type (Kruskal-Wallis chi-squared = 248.27, df = 7, p-value < 2.2e-16)

To see where the difference(s) are run a Dunn test Zar (2010) states that the Dunn test (in the FSA package) is appropriate for groups with unequal numbers of observations.(Zar, J.H. 2010. Biostatistical Analysis, 5th ed.  Pearson Prentice Hall: Upper Saddle River, NJ.) http://rcompanion.org/rcompanion/d_06.html

SAM WHEN DUNN IS INSTALLED, GO TO RCOMPANIONS.ORG AND LOOK FOR DUNN - CHECK CHROME HISTORY (PROBABLY UNDER KRUSKAL WALLIS) ALSO MAP THE DISTRIBUTION OF THESE GEAR TYPES
```{r}
pairwise.wilcox.test(presence$temp_depth, presence$gear, p.adj='bonferroni', exact=F)
```

dunn test (not working)
```{r}
gear_temp_depthdunn <- dunnTest(presence$temp_depth, presence$gear)

write.csv(gear_temp_depthdunn, "../output/env/gear_temp_depthdunn.csv", row.names = TRUE)
```
